---
title: "COVID-19"
subtitle: ""
author: "Du Shi,Zhe Xue,Kunning Zhang,Wenhui Zhang,Zhaojun Meng"
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
library(lubridate)
library(tidymodels)
library(ggplot2)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
worldometer_data <- read_csv("data/worldometer_data.csv")
usa_county_wise <- read_csv("data/usa_county_wise.csv")
full_grouped <- read_csv("data/full_grouped.csv")
day_wise <- read_csv("data/day_wise.csv")
covid_19_clean_complete <- read_csv("data/covid_19_clean_complete.csv")
country_wise_latest <- read_csv("data/country_wise_latest.csv")
qt <- read_csv("data/qt.csv")
usa_county_wise1 <- read_csv("data/usa_county_wise1.csv")
usa_county_wise2 <- read_csv("data/usa_county_wise2.csv")
```

```{r include=FALSE}
style_xaringan(
  title_slide_background_image = ""
)
```

class: center, middle,inverse

#DATASET:
#1 COVID-19 Dataset
#2 Covid-19 Temperature, Oxygen & Pulse Rate readings
#which were found on Kaggle
https://www.kaggle.com/datasets/imdevskp/corona-virus-report?search=COVID-19+DATASET
https://www.kaggle.com/datasets/rishanmascarenhas/covid19-temperatureoxygenpulse-rate
---
class: inverse

#Glimpses of our datasets

```{r echo=FALSE}
glimpse(full_grouped)
```

```{r echo=FALSE}
glimpse(usa_county_wise2)
```

---
class: inverse

```{r echo=FALSE}
glimpse(qt)
```

```{r echo=FALSE}
glimpse(country_wise_latest)
```



---

class: inverse, center, middle
#ORIGIN
A new coronavirus designated 2019-nCoV was first identified in 2019.
As of 30 January 2020, approximately 8,243 cases have been confirmed.
There are obvious changes in patients' vital signs.
---
class: inverse, middle, center
#1.World overview.

Graphing the number of confirmed cases and deaths.This gives us a big picture of the past COVID-19 in 2020.
---
class:inverse
The totally trend of the confirmed cases and deaths number in 2020 is showed in following two graphs.

```{r echo=FALSE}
full_grouped %>%
  ggplot(aes(x = Date , y = Confirmed)) +
  geom_line()+
  scale_x_date(date_breaks = "1 month",labels = date_format("%m"))+
  labs(title = "Number Of COVID-19 Cases Over Time",
       y = "Number of cases",
       x = "Months(from 2020-01-22)")+
  theme(panel.grid.major=element_line(colour=NA))+
  theme_bw()
```


---
class:inverse
The totally trend of the confirmed cases number in 2020 is showed below.

```{r echo=FALSE}
full_grouped %>%
  ggplot(aes(x = Date , y = Deaths)) +
  geom_line()+
  scale_x_date(date_breaks = "1 month",labels = date_format("%m"))+
  labs(title = "Number Of COVID-19 Deaths Over Time",
       y = "Number of deaths",
       x = "Months(from 2020-01-22)")+
  theme(panel.grid.major=element_line(colour=NA))+
  theme_bw()
```

---
class:inverse
Top 15 countries in the number of confirmed cases

```{r echo=FALSE}
country_wise_latest %>%
  arrange(desc(Confirmed)) %>%
  slice(1:15) %>%
  ggplot(aes(x = Confirmed , y = reorder(`region`,Confirmed),fill = `WHO Region`)) +
  geom_col()+
  geom_text(aes(label = Confirmed), 
            vjust = 0,
            size = 2,
            colour = "black") +
  labs(title = "Confirmed Cases Worldwide",
       y = "Country",
       x = "Number of confirmed cases")

```

---
class:inverse
Top 15 countries in the number of deaths
```{r echo=FALSE}
country_wise_latest %>%
  arrange(desc(Deaths)) %>%
  slice(1:15) %>%
  ggplot(aes(x = Deaths , y = reorder(`region`,Deaths),fill = `WHO Region`)) +
  geom_col()+
  geom_text(aes(label = Deaths), 
            vjust = 0,
            size = 2,
            colour = "black") +
  labs(title = "Deaths Cases Worldwide",
       y = "Country",
       x = "Number of deaths")
```

From all these graphs above,it is clear that COVID-19 began to spread in the world in April of 2020 and Americas region is the hardest-hit area in both deaths and confirmed number.

---
class:inverse,middle,center

#2.Recovery rate of COVID-19 in different countries
Recovery rates vary greatly from different country/Region
---
class:inverse

The recovery rate of the COVID-19 in 2022 for all countries in the world with data

```{r echo=FALSE, warning=FALSE}
worldometer_data %>% ggplot(aes(x = `Country/Region`, 
y = TotalRecovered / TotalCases, ))+ 
geom_bar(stat='identity',position='dodge')+
  labs(
    x = 'Selected Country',
    y = 'Percent of recovery',
    title = 'Recovery rate of COVID-19 in different countries')+
  theme(axis.text.x = element_blank())
```

---
class:inverse

Countries with low COVID-19 recovery rate

```{r echo=FALSE}
newdata<-subset(worldometer_data,TotalRecovered / TotalCases<0.25)
ggplot(newdata,aes(y = `Country/Region`, 
x = TotalRecovered / TotalCases))+ 
geom_bar(stat='identity',position='dodge', fill = 'Firebrick')+
labs(y = 'Selected Country',
     x = 'Percent of recovery',
     title = 'Recovery rate of COVID-19 in different countries')
```

---
class:inverse

Countries with high COVID-19 recovery rate

```{r echo=FALSE}
newdata<-subset(worldometer_data,TotalRecovered / TotalCases>0.98)
ggplot(newdata,aes(y = `Country/Region`, 
x = TotalRecovered / TotalCases))+ 
geom_bar(stat='identity',position='dodge', fill= 'Turquoise4')+
labs(y = 'Selected Country',
     x = 'Percent of recovery',
     title = 'Recovery rate of COVID-19 in different countries')
```

---
class:inverse,middle,center
#3. The map of covid distribution.


---
class:inverse
In this part, we'll first look at the worldwide distribute.
```{r echo=FALSE}
world <-country_wise_latest
mapdata<- map_data("world")
mapdata <- left_join(mapdata, world , by = "region")
mapdata1 <- mapdata %>% 
  filter(! is.na(mapdata$Confirmed))
map1<- ggplot(mapdata1,aes(x= long, y=lat, group=group))+
  geom_polygon(aes(fill= Confirmed), color="black")
map2<-map1 + scale_fill_gradient(name= "covid worldwide", high = "red", low = "green",na.value = "grey 60")+
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank())
map2
```

So, it is clear that in the year of 2020, south America suffered from covid-19 the most, followed by southern Asia.




---
class:inverse
```{r echo=FALSE}
usa <-usa_county_wise2
mapdata2<- map_data("state")
mapdata3 <- left_join(mapdata2, usa , by = "region")
mapdata4 <- mapdata3 %>% 
  filter(!is.na(mapdata3$Confirmed))
map1<- ggplot(mapdata4,aes(x= long, y=lat, group=group))+
  geom_polygon(aes(fill= Confirmed), color="black")
map2<-map1 +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank())
map2
```

From the map we can find that there at 4 remarkable bright blue area represented by the top four most populous states in America, which are California, Texas, Florida, and New York separately.
---
class:inverse,middle,center
#4.Predicting the probability of positive results

---
class:inverse
#Modeling

```{r echo=FALSE}
qt <- qt %>%
  select(Oxygen, PulseRate, Temperature,Result) %>%
  drop_na()

set.seed(1234)
qt_split <- initial_split(qt)
qt_train <- training(qt_split)
qt_test  <- testing(qt_split)

qt_rec_1 <- recipe(Result ~ ., data = qt)

qt_spec_1 <- logistic_reg() %>% 
  set_engine("glm")
  
qt_wflow_1 <- workflow() %>% 
  add_model(qt_spec_1) %>% 
  add_recipe(qt_rec_1)

qt_fit_1 <- qt_wflow_1%>% 
fit(data = qt_train)
tidy(qt_fit_1)

```

The probability of positive = 

exp(32.4 + (-1.15) * Oxygen +  0.0145	* Pulse Rate + 0.729 * Temperature)
_______
1+exp(32.4 + (-1.15) * Oxygen +  0.0145	* Pulse Rate + 0.729 * Temperature)

---
class:inverse
#Model checking

```{r echo=FALSE}
qt_pred<- predict(qt_fit_1, qt_test, type = "prob") %>% 
  bind_cols(qt_test)
qt_pred
```

---
class:inverse
#ROC curves
```{r echo=FALSE}
qt_pred %>%
  roc_curve(truth = as.factor(Result),
            .pred_Positive,
            event_level = "second") %>%
  autoplot()
```

---
class:inverse
#the areas under the ROC curves
```{r echo=FALSE}
qt_pred %>%
  roc_auc(truth = as.factor(Result),
          .pred_Positive,
          event_level = "second")
```

---
class:inverse

#Thanks！

