---
title: "COVID-19"
subtitle: ""
author: "Du Shi,Zhe Xue,Kunning Zhang,Wenhui Zhang,Zhaojun Meng"
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
library(lubridate)
library(tidymodels)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
worldometer_data <- read_csv("data/worldometer_data.csv")
usa_county_wise <- read_csv("data/usa_county_wise.csv")
full_grouped <- read_csv("data/full_grouped.csv")
day_wise <- read_csv("data/day_wise.csv")
covid_19_clean_complete <- read_csv("data/covid_19_clean_complete.csv")
country_wise_latest <- read_csv("data/country_wise_latest.csv")
qt <- read_csv("qt.csv")
```

```{r include=FALSE}
style_xaringan(
  title_slide_background_image = ""
)
```

class: center, middle,inverse

#DATASET: COVID-19 Dataset
#Covid-19 Temperature, Oxygen & Pulse Rate readings
#which were found on Kaggle
https://www.kaggle.com/datasets/imdevskp/corona-virus-report?search=COVID-19+DATASET
https://www.kaggle.com/datasets/rishanmascarenhas/covid19-temperatureoxygenpulse-rate
---
class: inverse


#These are glimpse of our dataset
```{r echo=FALSE}
glimpse(full_grouped)
```
---
class: inverse

```{r echo=FALSE}
glimpse(country_wise_latest)
```
---
class: inverse

```{r echo=FALSE}
glimpse(usa_county_wise)
```

---
class: inverse

```{r echo=FALSE}
glimpse(qt)
```
---

class: inverse, center, middle
#ORIGIN
Three years ago,a new coronavirus designated 2019-nCoV was first identified in Wuhan, the capital of China's Hubei province.
Transmission rate (rate of infection) appeared to escalate in mid-January 2020.
As of 30 January 2020, approximately 8,243 cases have been confirmed.
---
class: inverse, middle, center
#1.The country which was affected most.
---
class:inverse

A totally trend of the confirmed number in 2020 is showed below.
```{r echo=FALSE}
full_grouped %>%
ggplot(aes(x=Date,y=Confirmed,color=`WHO Region`)) +
geom_line()
       
```

From this graph,it is clear that COVID-19 began to spread in the world in April of 2020.



---
class:inverse
Top 15 countries


```{r echo=FALSE}
country_wise_latest %>%
  arrange(desc(Confirmed)) %>%
  slice(1:15) %>%
  ggplot(aes(x = Confirmed , y = reorder(`Country/Region`,Confirmed),fill = `WHO Region`)) +
  geom_col()+
  geom_text(aes(label = Confirmed), 
            vjust = 0,
            size = 3,
            colour = "black") +
  labs(title = "Confirmed Cases Worldwide",
       y = "Country",
       x = "Number of confirmed")
```




---
class:inverse,middle,center

#2.



---
class:inverse

---
class:inverse,middle,center
#3.Temperature, Oxygen and Pulse Rate readings of whether a patient was Positive or Negative.

---
class:inverse

```{r echo=FALSE}
qt <- qt %>%
  select(Oxygen,PulseRate,Temperature,Result) %>%
  drop_na()

set.seed(1234)
qt_split <- initial_split(qt)
qt_train <- training(qt_split)
qt_test  <- testing(qt_split)

qt_rec_1 <- recipe(Result ~ ., data = qt)%>%
  step_dummy(all_nominal(), -all_outcomes())

qt_spec_1 <- logistic_reg() %>% 
  set_engine("glm")
  
qt_wflow_1 <- workflow() %>% 
  add_model(qt_spec_1) %>% 
  add_recipe(qt_rec_1)

qt_fit_1 <- qt_wflow_1%>% 
fit(data = qt_train)
tidy(qt_fit_1)


```

The probability of COVID-19 positive = exp(32.38560261 + (-1.14948473)*Oxygen + 0.01447323*Pulse Rate + 0.72863310*Temperature)
---

# Plots 

```{r recode-species, echo = FALSE}
6
```

```{r plot-iris, echo = FALSE}
# Code hidden with echo = FALSE
# Uses modified iris dataset from previous chunk
# Play around with height and width until you're happy with the look

```

---

## Plot and text

.pull-left[
- Some text
- goes here
]
.pull-right[
```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
# see how I changed out.width and fig.width from defaults
# to make the figure bigger
ggplot(penguins, aes(x = bill_length_mm, y = species, color = species)) +
  geom_boxplot() +
  theme_minimal()
```
]

---

# Tables

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r iris-table, echo = FALSE}
kable(head(iris), format = "html")
```

---

# Images

```{r castle, echo = FALSE, out.width = "60%", fig.align = "center", fig.cap = "Image credit: Photo by Jörg Angeli on Unsplash."}
include_graphics("https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80")
```

Or you can also include a full page image. See next slide.

---

background-image: url(https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80)

---

# Math Expressions

You can write LaTeX math expressions inside a pair of dollar signs, e.g. &#36;\alpha+\beta$ renders $\alpha+\beta$. You can use the display style with double dollar signs:

```
$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$
```

$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$

Limitations:

1. The source code of a LaTeX math expression must be in one line, unless it is inside a pair of double dollar signs, in which case the starting `$$` must appear in the very beginning of a line, followed immediately by a non-space character, and the ending `$$` must be at the end of a line, led by a non-space character;

1. There should not be spaces after the opening `$` or before the clos
1. Math does not work on the title slide (see [#61](https://github.com/yihui/xaringan/issues/61) for a workaround).

---

# Feeling adventurous?

- Want to find out more about `xaringan`? See https://slides.yihui.name/xaringan/#1.

- You are welcomed to use the default styling of the slides. In fact, that's what I expect majority of you will do. You will differentiate yourself with the content of your presentation.

- But some of you might want to play around with slide styling. The 
`xaringanthemer` provides some solutions for this that: https://pkg.garrickadenbuie.com/xaringanthemer.

- And if you want more bells and whistles, there is also `xaringanExtra`: https://pkg.garrickadenbuie.com/xaringanExtra.
